\chapter{Conclusion / Results}
\label{chap:conclusions}
Overall the process of the preliminary study did not work out as expected. On one hand the technical requirements for the programming environment caused way more problems than expected and on the other hand, the time planning and focus of the author did get out of hand. The combination of these two issues caused major time and motivation problems. Therefore the result of the preliminary study is not satisfying for the author in accordance to the initial expectation.
Nevertheless, working on this project is very interesting and challenging, which means that the will to continue this project is unbroken.

Content wise there should have been a bigger accomplishment according the time given and the massive amount of time invested. After many hours of literature review, a sobering low amount of portable possibilities has been found. This leads to the conclusion that the way of research has to be adapted in order to find suitable solution for the existing issues.
Due to the adaption of the initial plan and the exchange with the experts, a realistic approach has been defined. Under consideration of all these factors, the best possible result is now provided.

The most important learning for the work on the milestones is to keep an strong focus on the actual tasks combined with a good and mindful time management. Also the exchange with other students and the experts shall be kept alive to benefit of the given knowledge. Help shall be searched at a earlier point of time, which does not mean, not to try to fix problems by the authors own possibilities and serious tries.

The definition of the milestones provides a promising planning of the Bachelor Thesis and seems to allow a good result for the main goal of the project. Needed Hardware and Software is mostly identified and methods to fulfill the requirements are described. 

An intense research of the topic and possible alternatives for occurred problems has been executed and leads to a knowledge which can be used and extended during the Bachelor Thesis.  

For the start of the Bachelor Thesis, only the learning will be taken into account and the disappointment is left behind. With great motivation and a strong will to perform well, the author is now looking forward to the realization of the milestones of the Bachelor Thesis. 